---
title: 'RMarkdown:  In Class Assignment'
author: "Brenda Nava"
date: "Data 2401"
output: 
  html_document:
    toc: TRUE
    toc_depth: 3
---


```{r setup, include=FALSE}
# Everything in this chunk is R code. 
# You are not expected to understand or edit this yet. 
# We will talk about what this does in a later class, with a little preview in part 2.
knitr::opts_chunk$set(echo = TRUE) 
```


Reminders: 

- You do not need to memorize Markdown syntax.
- You are expected to look things up using:
   - RStudio’s Markdown Help
   - Online documentation or examples
- Click Knit as you go to check that your document still renders correctly.
- Commit at the end, but consider committing as you go as well. 



# Part 1: Markdown Practice

**Do not skip reading this instruction** Create a new section at the end of this section named "Your work here". In that section, complete the tasks below:

- Make a *subsection* called Wise Words. 
- Put your favorite quote in a block quote. 
- Add a working, clickable link to a website that provides more information about that quote.
- Make another *subsection* called "I recommend", and add some information about your favorite author or musician: 
  - A _subsubheading_ with the name of the artist or author;    
  - An example of their writing or lyrics (formatted in a *block of text*);   
  - A _list_ of things they have written or performed (remember to use the formatting markup for a list!), with any of the titles/names in bold. 

# My work

## Wise words

"Believe you can and you're halfway there."

https://economictimes.indiatimes.com/magazines/panache/quote-of-the-day-by-theodore-roosevelt-believe-you-can-and-youre-halfway-there-/articleshow/126428365.cms




# I Recommend



## Ludwig van Beethoven: German composer and pianist

> Beethoven: Symphony No. 5 - Album by Ludwig van

## More song suggestions:
- Piano Sonata No. 14
- Symphony No. 9
- Piano Sonata No. 8
- Symphony No. 7
- Für Elise
- Symphony No. 3
- Symphony No. 6
- Piano Concerto No. 5
- Piano sonatas



  

# Part 2: Code Chunks

```{r echo = TRUE}
2 + 2

```

Complete the following steps:

- Knit the document and observe what appears in the output.
- Change the chunk option echo=TRUE to echo=FALSE.
- Knit the document again.
- Finally, write 2–3 sentences answering the following questions:
  - What changed between the two outputs?
  - Did the calculation still run when the code was hidden?
  - Why might someone want to hide code in a report?
  - Why might someone want to show code in a report?
  
## COMMENTS ON OUTPUT DIFFERENCES:

> On echo = TRUE, the equation was on display in the HTML file, whereas the echo = FALSE didn't execute the equation onto the HTML file. Granted, the equation was solved correctly in both instances. I think someone would want to hide the code for privacy reasons. On the other hand, someone would want to show the code to give further details. 
  
# Part 3: A small R-in-markdown preview

- Create a subsection within this section called About this document.
- Write 2–3 sentences describing what this document is and what it produces.
- Include one value generated by inline R code.

## About this document:

This document produces a versatile setting to execute both written explanations and R code. It also demonstrates how to hide and expose code [`r 2+2`],
``` {r echo = TRUE}
2 +2

```




# Submission date:
```{r echo = FALSE}


format(Sys.Date(),"%m/%d/%y")
       
```





> To include inline code, use this weird little `r 2+2` pattern, putting the code where I have 2+2 (which is code!) 
> You can use the function `Sys.Date()`, which would be added like this `r Sys.Date()` but you can do something else if you want. (Look at the knit html to see what this does.)

 

# Submitting Instructions

When you are finished: 

- Knit the document so that it produces an html file.
- Stage, commit, and push:
  - The updated `.rmd` file 
  - The generated `.html` file
- Submit the GitHub link to the assignment on Canvas.
 
